|

### 2023-03-22 paper/01-introduction.Rmd
created data section
Modify into to remove finalist mention

In recent years, tracking data have replaced traditional box-score statistics and play-by-play data as the state-of-the-art tool in sports analytics.
Numerous sports have been collecting and releasing data on player and ball locations on the playing surface over the course of a game.
This spatio-temporal multi-resolution source of data have provided exceptional opportunities for researchers to perform advanced studies at a more complex level to deepen the understanding of different sports.
For complete surveys on how tracking data have transformed sports analytics, see @Macdonald2020Recreating, @Baumer2023Big, and @Kovalchik2023Player.

@@

The first BDB led to several contributions largely focused offensive performance evaluation. For example. finalists @deshpande2020expected introduced an approach for modeling the hypothetical completional probability of a pass aiding in the evalaution of quarterback (QB) decision making. The winners of the inaugural BDB focused on identifying receiver routes via clustering techniques [@chu2020route] and convolutional neural networks [@sterken2019routenet]. Along with the BDB competition entries, the public release of NGS data allowed researchers to tackle a variety of other problems such as revisiting fourth down decision making [@lopez2020bigger], annotating pass coverage with gaussian mixture models [@dutta2020unsupervised], and introducing a continuous-time framework to estimate within-play value [@yurko2020going]. Since its inception, the BDB has changed themes each year leading to new insight about evaluating running backs, defensive backs, and special teams performance.

In this work, we present a novel approach to measure the performance of pass rushers (defensive players charging the QB) that was selected as a finalist for the [2023 edition of the NFL BDB](https://www.kaggle.com/competitions/nfl-big-data-bowl-2023), which asked participants to evaluate linemen on passing plays. Relative to other aspects of American football, such as QB evaluation [@burke2019deepqb, @reyers2021quarterback], the literature on evaluating pass rushers is scarce. Below, we provide a brief overview of existing pass rush metrics.

@@

>>>>

In recent years, tracking data have replaced traditional box-score statistics and play-by-play data as the state-of-the-art tool in sports analytics.Numerous sports have been collecting and releasing data on player and ball locations on the playing surface over the course of a game.
This spatio-temporal multi-resolution source of data have provided exceptional opportunities for researchers to perform advanced studies at a more complex level to deepen the understanding of different sports.
For complete surveys on how tracking data have transformed sports analytics, see @Macdonald2020Recreating, @Baumer2023Big, and @Kovalchik2023Player.

@@

The first BDB led to several contributions largely focused offensive performance evaluation. For example. finalists @deshpande2020expected introduced an approach for modeling the hypothetical completional probability of a pass aiding in the evalaution of quarterback (QB) decision making. The winners of the inaugural BDB focused on identifying receiver routes via clustering techniques [@chu2020route] and convolutional neural networks [@sterken2019routenet]. Along with the BDB competition entries, the public release of NGS data allowed researchers to tackle a variety of other problems such as revisiting fourth down decision making [@lopez2020bigger], annotating pass coverage with gaussian mixture models [@dutta2020unsupervised], and introducing a continuous-time framework to estimate within-play value [@yurko2020going]. Since its inception, the BDB has changed themes each year leading to new insight about evaluating different positions such as running backs, defensive backs, and special teams. The [2023 edition of the NFL BDB](https://www.kaggle.com/competitions/nfl-big-data-bowl-2023) continued this revolving theme by asking participants to evaluate lineman on passing plays.

In this work, using data made available in the 2023 BDB, we present a novel approach to measure the performance of pass rushers (defensive players charging the QB). Relative to other aspects of American football, such as QB evaluation [@burke2019deepqb, @reyers2021quarterback], the literature on evaluating pass rushers is scarce. Below, we provide a brief overview of existing pass rush metrics.

@@

Section \ref{sec:data}
